Spatiotemporal Data Classification

### 2017-12-29 Report/BigDataHomework1.tex
changes to report

	The above logic is implemented in the file CleanData.py in function filter\_trips. The two lists (trips\_too\_small and trips\_too\_big) will keep the excluded trips due to either not valid total distance or to invalid max distance between successive points. For each trip in the list (returned from question A) the total distance is calculate, using the function calculate\_lonlat\_distance, which returns the distance between two successive points using the haversine formula. Following the same logic, the max distance between successive points of a trip is calculated and a distance is found more than 2km, the trip is excluded.

@@

	\subsection{Question C}
	This task is implemented in the file DataVisualization.py and the created output is stored in the output folder in the gmplots directory. The requirement is to visualize five of the given train trips. For this purporse, a new trips list is creating containing five trips, excluding all trips with null journey\_id. Afterwards, the data\_visualization function is called, and a points list is created having two tuples with all the longitudes and latitudes(function idx\_to\_lonlat in the utils.py).

>>>>

	The above logic is implemented in the file CleanData.py in function filter\_trips. The two lists (trips\_too\_small and trips\_too\_big) will keep the excluded trips due to either not valid total distance or to invalid max distance between successive points. For each trip in the training dataset (in the dictionary format from question A) the total distance is calculate, using the function calculate\_lonlat\_distance, which returns the distance between two successive points using the haversine formula. Following the same logic, the max distance between successive points of a trip is calculated and a distance is found more than 2km, the trip is excluded.

@@

	\subsection{Question C}
	This task is implemented in the file DataVisualization.py and the created output is stored in the output folder in the gmplots directory. The requirement is to visualize five of the given train trips. For this purporse, after having excluded all trips with null journey\_id and with less than 1 lists with coordinates, the trips list is shuffled and then iterated only for 5 trips. Afterwards, a points list is created having two tuples with all the longitudes and latitudes(function idx\_to\_lonlat in the utils.py).
